---
title: "Final_Croptype"
author: "SuminChun"
date: "2024-11-22"
output: html_document
---
```{r}
library(dplyr)
library(ggplot2)
library(tidyverse)
```

### Import Dataset
```{r}
data <- read.csv("climate_change_impact_on_agriculture_2024.csv")
```

### Preparation and cleaning the data

```{r}
# mutate continent columns

country_to_continent <- data.frame(
  Country = c("Argentina", "Australia", "Brazil","Canada","China","France",
              "India","Nigeria", "Russia","USA"),
  Continent = c("South America", "Oceania", "South America", 
                "North America", "East Asia", "Europe", 
                "South Asia", "Africa","Eurasia","North America")
)

data_with_continent <- data %>%
  left_join(country_to_continent, by = "Country") 

data <- data_with_continent %>%
  select(Year, Country, Continent, Region, everything())
```

# Crop type 

1. Crop Yield vs Climate Variables

```{r}
crop_types <- unique(data$Crop_Type)
```

```{r}
ggplot(data, aes(x = Crop_Type, y = Crop_Yield_MT_per_HA)) +
  geom_violin(fill = "lightblue", color = "darkblue") +
  facet_wrap(~ Crop_Type, scales = "free_x") +
  labs(
    title = "Yield Distribution by Crop Type",
    x = "Crop Type",
    y = "Yield (MT/HA)"
  ) +
  theme_minimal()
```


2. Yield vs Average Temperature

i. Research Question:
How does the average temperature affect crop yield, and which crops are most resilient to temperature changes?

ii. Hypotheses:

Null Hypothesis (H0): Average temperature has no significant effect on crop yield, and there is no difference in resilience across crop types.

Alternative Hypothesis(Ha): Average temperature significantly affects crop yield, with some crop types showing greater resilience.

```{r}
ggplot(data, aes(x = Average_Temperature_C, y = Crop_Yield_MT_per_HA, color = Crop_Type)) +
  geom_line() +
  facet_wrap(~ Crop_Type, scales = "free") + 
  labs(
    title = "Yield vs Average Temperature by Crop Type",
    x = "Average Temperature (°C)",
    y = "Yield (MT/HA)"
  ) +
  theme_minimal()
```

3. Yield vs CO2 Emissions

i. Research Question: What impact do CO2 emissions have on crop yields, and which crops perform best under higher CO2 conditions?

ii. Hypotheses:

Null Hypothesis (H0): CO2 emissions have no significant effect on crop yield, and crop performance does not vary under different CO2 levels.

Alternative Hypothesis(Ha): CO2 emissions significantly affect crop yield, with certain crop types performing better under higher CO2 conditions.

```{r}
ggplot(data, aes(x = CO2_Emissions_MT, y = Crop_Yield_MT_per_HA, color = Crop_Type)) +
  geom_line() +
  facet_wrap(~ Crop_Type, scales = "free") +
  labs(
    title = "Yield vs CO₂ Emissions by Crop Type",
    x = "CO₂ Emissions (Million Tons)",
    y = "Yield (MT/HA)"
  ) +
  theme_minimal()
```


4. Yield vs Extreme Weather Events

i. Research Question: Is there a significant relationship between crop yield and the frequency of extreme weather events?

ii. Hypotheses:

Null Hypothesis (H0): There is no significant relationship between crop yield and extreme weather events.

Alternative Hypothesis(Ha): There is a significant relationship between crop yield and extreme weather events.

```{r}
ggplot(data, aes(x = Extreme_Weather_Events, y = Crop_Yield_MT_per_HA, color = Crop_Type)) +
  geom_point() +
  facet_wrap(~ Crop_Type, scales = "free") +
  labs(
    title = "Yield vs Extreme Weather Events by Crop Type",
    x = "Extreme Weather Events",
    y = "Yield (MT/HA)"
  ) +
  theme_minimal()
```

5. Yield vs Precipitation

i. Research Question: Is there a significant relationship between crop yield and precipitation levels?

ii. Hypotheses:

Null Hypothesis (H0): There is no significant relationship between crop yield and precipitation levels.

Alternative Hypothesis(Ha): There is a significant relationship between crop yield and precipitation levels.

```{r}
ggplot(data, aes(x = Total_Precipitation_mm, y = Crop_Yield_MT_per_HA)) +
  geom_bin2d() +
  facet_wrap(~ Crop_Type, scales = "free") +
  scale_fill_viridis_c() + 
  labs(
    title = "Yield vs Precipitation Heatmap by Crop Type",
    x = "Precipitation (mm)",
    y = "Yield (MT/HA)"
  ) +
  theme_minimal()
```

